---
title: "Comparing belief in free will and job satisfaction in the US and Taiwan "
author: 
  - Ismael Gharbi
  - Zackary Wais
Github Link: "Code and data are available at: https://github.com/zackaryrwais/Comparing-belief-in-free-will-and-job-satisfaction-in-the-US-and-Taiwan/blob/main/paper/references.bib"
date: 2024/02/12
date-format: long
abstract: "Free will and job satisfaction are some terminologies that you do not hear often in the same sentence; however go hand in hand with one another. This paper replicates the data compiled from three studies, the first one being in regards to Taiwanese real estate agents, the second study being American online labor workers, and the third study looking into the subject of free will and job satisfaction on an international level. We will also be applying secondary research to aid our understanding of this topic, and how cultural norms affect the responses we receive. As this is an issue that every individual thinks about before entering an industry or accepting a job, we found it to be a topic to be extremely beneficial to us as we are ending our time in university."
format: pdf
output-dir: "./output"
bibliography: references.bib

---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(knitr)
library(dplyr)
```


# Introduction {#sec-introduction}

	Free will is a topic that has different meanings depending on the city or 
	country we are in. For us in North America, the idea of free will is more 
	apparent according to a survey concluding that 60% of Americans believe that 
	they have free will (Scientific American 2015). With recent innovations in 
	fields such as psychology, philosophy, and science, the idea of free will has 
	shifted from what the exact term is, to free will’s effects on human beings. 
	This goes to show the neurological connections with free will, specifically 
	that the way we view free will, will later affect a variety of our daily 
	decision-making (Frontiers 2016).
	There are a variety of factors that shift the outcomes of free will, and in 
	this paper, we will take three different studies to help our understanding of 
	free will. The first study we are looking at takes 252 Taiwanese real-estate 
	agents over three months while examining their job satisfaction with free 
	will. The second study takes 137 American workers who are in an online labor 
	market and conducts the same study over six months. The estimand here for the 
	belief in free will would be the The Rakos et al and the full scale for the 
	second study, as for the Job satisfaction it is the adaptation of the five
items short scale of Brayfield and Rothe (1951) constructed by Judge, Locke, 
Durham, and Kluger (1998). Those scales are shown here from 0 to 10 for the sake
of simplicity.

	This subject has different meanings in every country, when taking a look at 
	countries outside of North America such as Asia and other Western countries, 
	they have different beliefs of free will on average, specifically that it is 
	not as important as North Americans view it (Frontiers 2017). At its core, 
	free will is to what extent or ability we can our own decisions and have 
	autonomy, as well as the outcomes and consequences of our actions. Studies 
	have shown that when free will is present, the population is happier, more 
	positive, and lives better, contrary to countries that do not have free will 
	(Alquist, Ainsworth, & Baumeister, 2013). Now this idea directly relates to 
	careers, as it is something that individuals spend a majority of their time 
	doing, and would prefer to be happier doing it rather than not being happy. 
	When you have autonomy and free will in your career, you immediately have a 
	higher job satisfaction, as your neurological decision-making is seen in a 
	much clearer manner. 




# Data {#sec-data}

## 2.1 Source
	The paper we have used for replication is from the list of Gilad Feldman 
	papers offered from the course, specifically titled Agency Beliefs Over Time 
	and Across Cultures: Free Will Beliefs Predict Higher Job Satisfaction, 
	written by Gilad Feldman, Jiing-Lih Farh, and Kin Fai Ellick Wong. This paper 
	dives into the meanings of free will, and takes several studies examining its 
	correlation with job satisfaction as the primary factor, but also includes 
	ideas in regards to psychological well-being and international perspectives. 
	Our reproduction seeks to focus on two different findings made from the 
	original paper and apply a holistic lens to it. 
	The two claims we are focusing on are as follows: (1) Assessing the direction 
	of the relationship between belief in free will and job satisfaction. 
	(2) Evaluating the impact of cultural contexts on the perception of free will
	on indivudals throughout different professions and age groups. 

## 2.2 Methodology 
	This paper replicates the data that was originally studied for the (2018) 
	paper Agency Beliefs Over Time and Across Cultures: Free Will Beliefs Predict 
	Higher Job Satisfaction. The first study takes Taiwanese real estate agent’s 
	job satisfaction into account and conducted the study in 54 branch offices of 
	a public real estate company based in Taiwan. They then proceeded by
	distributing the surveys to agents in each of the branches at two different 
	times, once every 3 months for a total of 6 months of data. They ended up with
	293 surveys to review for study #1. For study number #2, the paper looks into 
	the Amazon Mechanical Turk (MTurk) American Worker’s Job Satisfaction. 
	The study was conducted in two different sections, in which they were able 
	to survey a total of 209 American participants. After this initial study was 
	done, the same group was invited to conduct a follow-up survey six months 
	later and took in responses over 15 days. Out of the 209 initial participants,
	only 137 of them conducted the follow-up survey. And for the final study, 
	contrary to the first two where they directly went to a group and surveyed 
	them; the surveyors used previous data from the World Value Survey (WVS) which
	was data conducted between 1990 and 2008, looking into the participant's views
	on free will, job satisfaction, and job autonomy. Over these 18 years, 
	the survey received data 257,597 people, and focused on 14,062 participants as
	they answered questions directly related to our research. Although the total 
	survey took into account people from over 40 countries, for our focus 
	we looked at individuals from 16 specific countries. 
	
## 2.3 Features 
	The studies conducted each had their specific variables conducted. 
	For the first study, the survey takes into account age, gender, social 
	desirability of the job, job satisfaction after the first wave of surveys, job satisfaction after the second wave of surveys, and their beliefs on free will. 
	The age range for this study was between 22 to 49 years old, and only took 
	into account male and female genders. The second study primarily took free 
	will and job satisfaction into account.
	


# Results

Data from Study 1 were used to show the relative amount of belief in free will 
of the average Taiwanese real estate agents and how much are they satisfied with
their job across two times within three months with the same sample.
We extracted the responses from the survey and extracted the responses to the 
questions : "From the scale of 0 to 10, How much do you agree with this 
statement: I have free will"and "From the scale of 0 to 10, How much do you 
agree with this statement: I am satisfied with my job" at Time one and two.
In Table 1, there are three values on a scale of 0 to 10 compared : 
(1) Job Satisfaction T1, (2) Job Satisfaction T2, and (3) Belief in Free Will.
The rows would be the mean and standard deviation calculated using R.
Looking at Table 1, we immediately notice that the mean score of Job 
satisfaction barely vary from the first and second time (5.64 and 5.74 
respectively) and that the average level of belief of free will would be 3.99. 
In addition,the standard deviation of the three values seem reasonable.
While analyzing Table 1, we can recognize that the slight increase in job
satisfaction still largely within the standard deviation which confirms the 
accuracy of the measurement that barely varies over the time.


Table 1 : Mean and standard deviation of belief in free will and 
job satisfaction within the Taiwanese real estate agency.
```{r, hide_code=TRUE}

Table_I <- data.frame(
  Job_satisfaction_T1 = c(5.64, 1.18),
  Job_satisfaction_T2 = c(5.74, 0.99),
  Belief_free_will = c(3.99, 0.49)
)

# Name the rows
rownames(Table_I) <- c("Mean", "Standard Deviation")

# Print the dataframe
print(Table_I)

```


Moving to the United States, Study 2 ,conducted in 2017, asked workers available 
on MTurk, a professional network spanning multiple professions the same 
questions as in Study 1 :  "From the scale of 0 to 10, How much do you agree 
with this statement: I have free will"and "From the scale of 0 to 10, How much 
do you agree with this statement: I am satisfied with my job". The respondents'
answers were extracted and had their average and standard deviation as given 
in Table 2. This table compares two values on a scale of 0 to 10  : 
(1) Job Satisfaction T1 (2) Belief in Free Will. The rows would be the mean and
standard deviation calculated using R. Looking at Table 1, we see  that the mean
score of Job satisfaction is 5.29 and that the average level of belief of free 
will would be 5.28. The standard deviation of the three values seem reasonable.


Table 2 : Mean and standard deviation of belief in free will and job
satisfaction within Amazon Mechanical Turk American Workers.
```{r, hide_code=TRUE}

Table_II <- data.frame(
  Job_satisfaction = c(5.29, 1.22),
  Belief_free_will = c(5.28, 0.84)
)


rownames(Table_II) <- c("Mean", "Standard Deviation")


print(Table_II)
```

Graph 1 below with a y-axis depicting the US and Taiwan at Time 1 and 2 and a 
x-axis depicting a scale from 0 to 10. Both country has two bars measured on 
the scale depicting the belief in Free Will and the job satisfaction. We can 
observe that the average american worker has a higher belief in Free Will (5.28)
compared to his Taiwanese counterpart (3.99) but a relatively smaller job
satisfaction (5.64 and 5.74 compared to 5.29 in the US). This may suggest a low 
negative to no correlation between belief in Free Will and Job Satisfaction due
to the different circumstances of the samples.


Graph 1 : Bar Chart comparing the average belief in free will and job
satisfaction between MTurk American Workers and employees in Taiwan.

```{r, hide_code=TRUE}

library(ggplot2)
library(dplyr)

# Sample data
data <- data.frame(
  Country = rep(c("US", "Taiwan T1", "Taiwan T2"), each = 2),
  Value = c(5.28, 5.29, 3.99, 5.64, 3.99, 5.74), # Sample values ranging from 0 to 10
  Type = rep(c("Belief in Free Will", "Job Satisfaction"), 3)
)


# Plotting
ggplot(data, aes(x = Country, y = Value, fill = Type)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(limits = c(0, 10)) +
  labs(x = "Country", y = "Scale") +
  theme_minimal() +
  scale_fill_manual(values = c("Belief in Free Will" = "blue", "Job Satisfaction" = "red")) 


```





# Replication:
Link of the reproduction of the paper on the social science reproduction 
platform :https://doi.org/10.48152/ssrp-1yg9-0z41




# Discussion

## 4.1 Findings 
	In this paper, we have replicated the studies and results found by Feldman, 
	Farh, and Wong. These authors sought to find the relationships between free 
	will and job satisfaction across different countries, cultures, and ages. Of 
	these findings, our paper focused on three specific aspects.
	(1) Free will is fairly constant throughout the first study, and there is an 
	increase in job satisfaction over time. 
	(2) Individuals with a stronger belief in free will, will also report a higher
	job satisfaction in a single region. 
	(3) Depending on the region you are in, individuals will report different 
	beliefs in free will correlated to job satisfaction.

## 4.2 Canada’s belief in free will and job satisfaction
	The Canadian population is currently at just over 38 million people and has 
	increased by nearly 4 million people in the past decade. Among all of the 
	provinces in Canada, Quebec is the province with the highest overall
	satisfaction among men and women in Canada (Statistics Canada 2023). Among 
	this group, Quebec men surveyed that they were 80.7% very satisfied or 
	satisfied with their job, and Quebec women only surveyed 78.4% being either 
	very satisfied with their job or satisfied with it. Among the women, the 
	province of New Brunswick holds the highest job satisfaction topping in at 
	80.5%, with Prince Edward Island being the runner-up at 80%. 
	Concerning the original paper from Feldman, Farh, and Wong, it is important to
	note the international presence and multicultural aspect of this study, as 
	well as the vast number of immigrants that move to Canada every year. In the 
	year 2023, Canada was able to welcome over 437,000 new permanent residences, 
	and 604,000 temporary workers, with a variety of these individuals coming from
	Asia and Europe (Government of Canada 2023). Due to this vast number of 
	immigrants coming to Canada, we can assume that there were a variety of 
	individuals that experienced an increase in belief in free will with their 
	correlation to job satisfaction especially those that came from countries 
	where belief in free will was weaker than that of Canada. Contrarily, those 
	that came from countries with a stronger belief in free will and came to a 
	specific province in Canada with a lower job satisfaction such as Manitoba 
	with a 65.2% job satisfaction (Statistics Canada 2023), might experience a 
	reverse effect and decrease in their belief in free will which would directly 
	correlate to their job satisfaction. 

## 4.3 Practical Implications for Organizations 
	The research and work done by Feldman and his peers will allow companies and organizations worldwide to drastically benefit their organizations by taking 
	into account their employee's views on their current job statuses. By taking 
	employee considerations into account, employee retention will be higher 
	because job satisfaction will increase, companies will increase their overall 
	reputation and image, and the overall well-being of companies will rise with 
	an increase in company loyalty. Once these institutions realize that stronger 
	job satisfaction stems from a stronger belief in free will, employees will be
	able to foster a state of autonomy, ultimately empowering employees and 
	enhancing the overall productivity of respective companies. 

## 4.4 Limitations 
	As the work we conducted was based on the reproduction from the work of 
	Feldman, we were limited to the parameters he looked into. Despite the data 
	being long and expansive, we could only look at the data from the United 
	States and Taiwan specifically. There were also some concerns in regards to 
	the accuracy of data, specifically that some of the individuals who partook 
	in the surveys were either influenced to say positive things about the company
	or were led to believe that they have free will, whereas, in reality, they do 
	not. This is a topic that is much more apparent in an international setting, lower-developed communities, and areas with less free speech. 
	Additionally, there was the issue of the variety in occupations, where we 
	would compare a white-collar executive working in a major American city such 
	as New York or San Francisco, to an employee at a much smaller company living 
	in Taiwan. There was no main base here to compare the two career paths as they
	are drastically different in every way. 
	Finally, we found that the reproducible article focused on many positive 
	outcomes of free will in the context of job satisfaction, and failed to 
	mention enough information in regard to the downside of the the lack of 
	autonomy and free will, and how that correlates with job satisfaction. The 
	role of employees in these instances does indeed vary as for many they account
	for their work ethic with happiness, disregarding autonomy and free will. This
	ultimately leads to ethical and moral issues that were not mentioned in the 
	paper. 
## 4.5 Future Research 
	In regards to future understandings of the topic of free will and job 
	satisfaction, it would be interesting to explore how ethics and morality 
	play a role in decision-making when it comes to individual autonomy. 
	Especially how specific work environments alter answers to research studies 
	and surveys. Additionally looking into different cultures and countries 
	outside of the United States and Taiwan, looking into major global cities 
	such as London, and remote areas such as Nunavut. Finally to take the study 
	to the next step would be to track an individual's opinions on this topic from 
	the beginning of their career to the end, ideally staying within the same 
	company for that time, looking at decades of research and studies. This would 
	be able to tap into the psychological implications of individuals and how 
	personality growth and maturity play a role in their decision-making process. 


\newpage


# References

"Site Survey Shows 60 Percent Think Free Will Exists; Read Why." *Scientific American Blog Network*, Scientific American, [February 12, 2024]. https://blogs.scientificamerican.com/talking-back/site-survey-shows-60-percent-think-free-will-exists-read-why/.

"Where Belief in Free Will Is Linked to Happiness." *Frontiers in News*, Frontiers, 24 January 2017, https://www.frontiersin.org/news/2017/01/24/where-belief-in-free-will-is-linked-to-happiness/.

"Table 1 Police-reported cybercrime, by type of violation, Canada, provinces and territories." *Statistics Canada*, Government of Canada, [Access Date], https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=4510008801.

"Annual Report to Parliament on Immigration 2023." *Immigration, Refugees and Citizenship Canada*, Government of Canada, 2023, https://www.canada.ca/en/immigration-refugees-citizenship/corporate/publications-manuals/annual-report-parliament-immigration-2023.html#.

Lavazza, Andrea, and Inglese, S. "Free Will and Neuroscience: From Explaining Freedom Away to New Ways of Operationalizing and Measuring It." Frontiers in Psychology, vol. 11, 2020, www.frontiersin.org/articles/10.3389/fpsyg.2020.00120/full. Accessed 14 Feb. 2024.

Wagner, H. "Why We Have Free Will." Scientific American, 6 Jan. 2016, www.scientificamerican.com/article/why-we-have-free-will/. Accessed 14 Feb. 2024.

Ghose, Tia. "Is Free Will an Illusion? Scientists, Philosophers Forced to Differ." Live Science, 3 May 2013, www.livescience.com/29100-illusion-of-free-will.html. Accessed 14 Feb. 2024.










